A survey of HTTP caching options on the open Web

### 2014-12-18 sanity/paper1.tex
Move details into appendix
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@911 43ef1190-90fd-4dd7-a769-d0121f02b80e

Then, we retrieved the dataset of the Billion Triple Challenge
2014\todo{ref}, a 4~GTriple corpus of spidered Web data. To compile a
list of interesting candidates to further examine, we performed a
series of data reduction steps, manually inspecting the result between
each step. Due to the presence of invalid RDF, we
iterated through the NQuad files on a line-by-line basis. First, we
matched each line against a regular expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework RDF::Trine\todo{footnote} was used to parse
the line. Lines that failed to parse was discarded. We have not
investigated whether this could introduce biases. Statements were then
accepted into a new NQuad file if they had a predicate that matched
the \rdfterm{sd:endpoint}\todo{footnote} or matched a case-insensitive
regular expression \texttt{sparql} if the subject and objects were
both resources, or the predicates \rdfterm{void:vocabulary},
\rdfterm{rdfa:vocabulary} or \rdfterm{api:vocabulary} \todo{footnotes
  for all}, as well as having an resource as object. Finally,
statements with the the classes \rdfterm{cogs:Endpoint},
\rdfterm{owl:Ontology} and \rdfterm{voaf:Vocabulary} \todo{footnotes for
  all} in the object position were also accepted. More classes and
properties were considered, but not used in the data reduction if they
did not occur in the original data.

>>>>

To examine as many different implementations and hosts as possible, we
noted that the Billion Triple Challenge
2014\todo{ref} dataset consisted of a 4~GTriple corpus of spidered Web data. To compile a
list of interesting candidates to further examine, we performed a
series of data reduction steps, manually inspecting the result between
each step. The details of this process is given in Appendix~\ref{app:reduction}.

\section{Implementation details\todo{proper formatting}}\label{app:reduction}

The Billion Triple Challenge 2014 dataset provided data in the form of
NQuad files. Due to the presence of invalid RDF, we iterated through
the NQuad files on a line-by-line basis. First, we matched each line
against a regular expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework RDF::Trine\todo{footnote} was used to parse the
line. Lines that failed to parse was discarded. We have not
investigated whether this could introduce biases. Statements were then
accepted into a new NQuad file if they had a predicate that matched
the \rdfterm{sd:endpoint}\todo{footnote} or matched a case-insensitive
regular expression \texttt{sparql} if the subject and objects were
both resources, or the predicates \rdfterm{void:vocabulary},
\rdfterm{rdfa:vocabulary} or \rdfterm{api:vocabulary} \todo{footnotes
  for all}, as well as having an resource as object. Finally,
statements with the the classes \rdfterm{cogs:Endpoint},
\rdfterm{owl:Ontology} and \rdfterm{voaf:Vocabulary} \todo{footnotes
  for all} in the object position were also accepted. More classes and
properties were considered, but not used in the data reduction if they
did not occur in the original data.
